DeepSphere: a graph-based spherical CNN

### 2019-09-25 main.tex
small edits

\section{Introduction [2 pages]}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{figure_architecture_v3}
	\caption{Example architecture from \cite{perraudin2019deepspherecosmo}.
		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
		Dense tasks (when the output lives on the sphere, like segmentation) are rotation equivariant.
		\todo{Shall we keep this figure? It's very nice, but we could save space. ML people probably have this in mind.}
	}
	\label{fig:architecture}
\end{figure}

DeepSphere leverages graph convolutions to achieve the following properties: (i) computational efficiency, (ii) sampling flexibility, and (iii) rotation equivariance (\secref{equivariance}).
An example architecture is shown in \figref{architecture}.
The main idea is to model the discretized sphere as a graph of connected pixels: the length of the shortest path between two pixels is an approximation of the geodesic distance between them.
We use the graph CNN formulation introduced in \citep{defferrard2016graphnn}, and a pooling strategy that exploits hierarchical pixelizations of the sphere.

>>>>

\section{Introduction}

@@

% \begin{figure}
% 	\centering
% 	\includegraphics[width=\linewidth]{figure_architecture_v3}
% 	\caption{Example architecture from \cite{perraudin2019deepspherecosmo}.
% 		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
% 		Dense tasks (when the output lives on the sphere, like segmentation) are rotation equivariant.
% 		\todo{Shall we keep this figure? It's very nice, but we could save space. ML people probably have this in mind.}
% 	}
% 	\label{fig:architecture}
% \end{figure}

DeepSphere leverages graph convolutions to achieve the following properties: (i) computational efficiency, (ii) sampling flexibility, and (iii) rotation equivariance (\secref{equivariance}).
% An example architecture is shown in \figref{architecture}.
The main idea is to model the discretized sphere as a graph of connected pixels: the length of the shortest path between two pixels is an approximation of the geodesic distance between them.
We use the graph CNN formulation introduced in \citep{defferrard2016graphnn}, and a pooling strategy that exploits hierarchical pixelizations of the sphere.
